Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-03-29 paper/paper.tex
More data

@@

We instead use a maximum clique algorithm. There has been a lot of recent
research on this
.

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-33}
    \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, the best
    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
    instances with these runtimes.} \label{figure:unconnected-33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-plain}
    \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, the best
    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
    instances with these runtimes.} \label{figure:unconnected-plain}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-undir33}
    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
        the cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the best clique approach compared to the best constraint programming approach: the colour at a point
        indicates the number of instances with these runtimes.} \label{figure:connected-undir33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
    cumulative number of instances solved by each approach, in under a certain time. On the bottom,
    the best clique approach compared to the best constraint programming approach: the colour at a point indicates the
    number of instances with these runtimes.}
\label{figure:connected-plain}
\end{figure}

>>>>

?? More? Can we scale to some of the SIP graphs?

@@

We instead use a maximum clique algorithm.

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-33}
    \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, an
    instance-by-instance comparison of the two approaches: the colour at a point indicates the
    number of instances with these runtimes.} \label{figure:unconnected-33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-plain}
    \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, an
        instance-by-instance comparison of the two approaches: the colour at a point indicates the
    number of instances with these runtimes.} \label{figure:unconnected-plain}
\end{figure}

@@

\paragraph{Does connected make instances easier or harder?} We could plot connected vs not connected
difficulties, and result sizes?

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-undir33}
    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
        the cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the association graph approach compared to the constraint programming approach with
        both branching and filtering.} \label{figure:connected-undir33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
        cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the association graph approach compared to the constraint programming approach
    with both branching and filtering.}
\label{figure:connected-plain}
\end{figure}
